---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regexcite

<!-- badges: start -->
<!-- badges: end -->

The goal of regexcite is to ...

## Installation

You can install the development version of regexcite from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pmanoharan-hr/regexcite")
```

## Example

An example when you can use `regexcite::str_split_one()`

```{r example}
library(regexcite)
## basic example code

x <- "alpha,bravo,charlie,delta"
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")

```
Notice how the return value is a **list** of length one, and the first element has the character vector.
This is inconvenient, i.e. we want the un-listed version which should be just the character vector.

That's exactly what `regexcite::str_split_one()` does.

```{r}
library(regexcite)

str_split_one(x, pattern = ",")
```

Use `str_split_one()` when the input is known to be a single string.
For safety, it will error if its input has length greater than one.

`str_split_one()` is built on `stringr::str_split()`, so you can use its `n` argument and stringr's general interface for describing the `pattern` to be matched.

```{r}
str_split_one(x, pattern = ",", n=2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```
